### 2021-09-13 documentos/pce.tex
etc

Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}. Given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.

@@

A remarkable consequence of positivity

>>>>

Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}. This is, given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.

@@

It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=1/2^N\tr\left( \sigma_i \mcE[\sigma_j]
 \right)$
